An Overview of Distributed Version Control Systems

### 2010-06-08 laarsample.tex
Creada nueva seccion de comparación de DVCS porque el contenido que estaba al principio de comparison quedaba re colgado. Agregados más paragraph breaks y toqué algo en las conclusiones.

\section{Comparison}
There are several DVCS in the market nowadays and most of them are open, free or have a free license while not being used in comercial environments. While most of them have very similar features, the one that has the greatest number if features is Git with over 150 commands out-of-the-box but at the same time it is the one with the steepest learning curve because it is very different from SVN, which is probably the most widely used VCS. 
One key aspect of VCS is its performance. It was said previously in this document that the merging process was crucial for a DVCS because it's something that you'll probably have to do several times during a day in a distributed environment and therefore it should be as fast as possible. This is not the case for all DVCS tools. In the following charts\cite{dvcsperfcomparison} we'll compare some of the most widely used DVCS.

\subsection{Commits}
In a DVCS the nature of the commits is different to centralized VCS, since commits are made in the local repository only. 
Commiting in centralized VCS means ``to share the change with everyone that queries the centralized server'' while in a 
DVCS means to store a change in the history, which is not shared until it's pushed or pulled into another repository.

@@

%----------------------------------------------------------------------
% SECTION IV: Then, why should I use it in my project?
%----------------------------------------------------------------------

@@

%Si mi proyecto es apto para aplicar la herramienta por qué debería utilizarla en 
%vez de utilizar CVS/SVN/otros, mostrando los costos y ventajas y desventajas,
% siempre desde el punto de vista "closed source" (debatible).
%\subsection{Should I use it in my project?}
Does everybody need these features? Speed, offline working, 
and easyness of branching/merging are nice features even if you work simply pulling 
and pushing changes against a central repository and not every peer out there. In some 
projects and with some tools, the advantage of going distributed may not be clear. 
For starters, in many closed source projects there is no need nor desire to have anything
other than centralized repositories, and while you can use a DVCS with a centralized
repository, there may not be enough to gain to balance the cost of changing. Distributed 
versioning \emph{is} more complex, and there is a ``conceptual overhead'' in the usage 
of it, even if most of the time you can ignore most features and use just what you need 
(even for one person proyects, Git and Mercurial may be easier to use than SVN).

The general lack of maturity in the tools is also a disadvantage, since the most flexible
way of working is the command-line interface. This makes it a bit harder to use because there 
are many commands, and they have a lot of options and some problems may not have an intuitive 
solution. There is more to learn and to use.

>>>>

\section{COMPARISON BETWEEN CENTRALIZED AND DISTRIBUTED}
\subsection{Commits}
In a DVCS the nature of the commits is different to centralized VCS, since commits are made in the local repository only. 
Commiting in centralized VCS means ``to share the change with everyone that queries the centralized server'' while in a 
DVCS means to store a change in the history, which is not shared until it's pushed or pulled into another repository.

@@

%----------------------------------------------------------------------
% SECTION IV: Then, why should I use it in my project?
%----------------------------------------------------------------------
\section{DVCS COMPARISONS}
There are several DVCS in the market nowadays and most of them are open, free or have a free license while not being used in comercial environments. While most of them have very similar features, the one that has the greatest number if features is Git with over 150 commands out-of-the-box but at the same time it is the one with the steepest learning curve because it is very different from SVN, which is probably the most widely used VCS. 
One key aspect of VCS is its performance. It was said previously in this document that the merging process was crucial for a DVCS because it's something that you'll probably have to do several times during a day in a distributed environment and therefore it should be as fast as possible. This is not the case for all DVCS tools. In the following charts\cite{dvcsperfcomparison} we'll compare some of the most widely used DVCS.

@@

%Si mi proyecto es apto para aplicar la herramienta por qué debería utilizarla en 
%vez de utilizar CVS/SVN/otros, mostrando los costos y ventajas y desventajas,
% siempre desde el punto de vista "closed source" (debatible).
%\subsection{Should I use it in my project?}
Does everybody need these features? Speed, offline working, 
and easyness of branching/merging are nice features even if you work simply pulling 
and pushing changes against a central repository and not every peer out there.

In some 
projects and with some tools, though, the advantage of going distributed may not be clear. 
In many closed source projects there is no need nor desire to have anything
other than centralized repositories, and while you can use a DVCS with a centralized
repository, there may not be enough to gain to balance the cost of changing.

Distributed versioning \emph{is} more complex, and there is a ``conceptual overhead'' in the usage 
of it, even if most of the time you can ignore most features and use just what you need 
(even for one person proyects, Git and Mercurial may be easier to use than SVN).

The general lack of completness in the tools is also a disadvantage, since the most flexible
way of working is the command-line interface. This makes it a bit harder to use because there 
are many commands, and they have a lot of options and some problems may not have an intuitive 
solution. There is more to learn and to use, even though some GUIs may help with these issues.
